\documentclass[a4paper, 12pt]{article}
%\usepackage[pdftex]{graphicx}
\usepackage[left=2cm,right=2cm,
    top=1.7cm,bottom=1.7cm,bindingoffset=0cm]{geometry}
    \usepackage[colorlinks=false]{hyper ref}
%\usepackage{beamerthemesplit}
%\usetheme{boxes}

\usepackage{longtable}

\usepackage{amscd}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{graphicx, titlesec}

    \newtheorem{conjecture}{Conjecture}
      \newtheorem{theorem}{Theorem}
      \usepackage{paralist}

\usepackage[usenames]{color}
\usepackage{colortbl}

\sloppy


 \usepackage{setspace}

%\renewcommand{\baselinestretch}{1}

\usepackage{environ}% http://ctan.org/pkg/environ

\newcounter{itemnum}
\NewEnviron{outeritem}{% Solution
   \stepcounter{itemnum}%
   {\item \BODY}%
}
\makeatletter
\newcommand{\advancecompactenumlevel}{\advance\@enumdepth\@ne}
\makeatother

\usepackage{setspace}
\singlespacing
\title{Curriculum Vitae}
%\onehalfspacing
\begin{document}
%\thispagestyle{empty}



%\textit{\Large \flushleft Anton Izosimov}
\begin{center}
{\centering{ \Large \textbf{Anton Izosimov -- Curriculum Vitae}}}\\ \noindent\hrulefill 
\end{center}\par
\begin{tabular*}{0.95\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
%\hline 
\parbox{0.4\linewidth}{Associate Professor \\ Department of Mathematics\\
University of Arizona}  & \parbox{0.4\linewidth}{email: izosimov@arizona.edu} 

\end{tabular*} \par


\par
\quad\par\bigskip
%\textbf{RESEARCH INTERESTS}\par\smallskip
% Geometry and dynamics, in particular integrable systems and geometric fluid mechanics \par\quad\par\smallskip
\textbf{{EDUCATION}}\par\smallskip
\begin{compactitem}
\item Loughborough University, PhD in Mathematics, 2012 \\
 Thesis title: {Singularities of bi-Hamiltonian systems and the multidimensional rigid body} \\  Advisor: Alexey Bolsinov 
\item   Moscow State University,  Candidate of Sciences in Mathematics,  2011 \\ 
Thesis title: {{Focus-focus singularities of integrable Hamiltonian systems}} \\
  Advisors: Alexey Bolsinov, Andrej Oshemkov
\item  Moscow State University, MS with honors in Mathematics, 2008
\end{compactitem}
\par\quad\par\smallskip
\textbf{EMPLOYMENT}\par\smallskip
\begin{compactitem}
%&\\
\item University of Glasgow, Reader, 2025 - present
\item University of Arizona, Assistant and Associate Professor, 2018 - 2025
\item University of Toronto, Postdoctoral Fellow, 2014 - 2017 \
%&\\
\item   National Research University Higher School of Economics, Docent, 2013 - 2014 
 %&\\

\item Moscow State University, Assistant Professor,  2012 - 2014\
% \centering 2007 - 2008 &{Abbyy}, Optical character recognition software developer \\
 \end{compactitem}
 \par\quad\par\smallskip
\textbf{VISITING POSITIONS}\par\smallskip
\begin{compactitem}
 \item Max Planck Institute for Mathematics, January - August 2025
 \item Max Planck Institute for Mathematics, June - December 2017
\item Hausdorff Research Institute For Mathematics, January - April 2012 %, \\\textbf{Integrability in Geometry and Mathematical Physics} trimester
\end{compactitem}
%\thispagestyle{empty}
\par\quad\par\smallskip
\textbf{TEACHING EXPERIENCE}\par\smallskip
\begin{compactitem}
\item University of Glasgow:  Core Skills,  Introduction To Real Analysis
\item University of Arizona \begin{compactitem} \item Undergraduate: Calculus I and II, Formal Mathematical Reasoning and Writing,  Introduction to Linear Algebra, ODEs and Stability Theory, Real Analysis, Theory of Complex Variables, Theory of Probability, Theory of Statistics \item Graduate: Algebra, Complex Analysis, Geometry and Topology, Symplectic Geometry and Integrable Systems, Theory of Graphs and Networks\end{compactitem}
\item University of Toronto: Calculus, Differential Equations, Groups and Symmetry, Linear Algebra, Real Analysis
\item Higher School of Economics: Calculus, Linear Algebra
\item Moscow State University: Geometry and Topology
\end{compactitem}
\par\quad\par\smallskip
\textbf{SELECTED AWARDS, GRANTS, AND SCHOLARSHIPS}\par\smallskip
\begin{compactitem}
\item Simons Foundation Travel Support for Mathematicians, 2024 - 2029
\item NSF Research Grant, 2020 - 2024
\item  F.V.\,Atkinson Teaching Award, University of Toronto, 2016
\item Best Instructor Award, Higher School of Economics, 2014
\item Dynasty Foundation Scholarship, Russia, 2013 - 2014 
\item Russian Foundation of Basic Research Grant, 2012 - 2013 
\item  {{Overseas Research Scholarship}}, United Kingdom, 2008 - 2011
\item  {{Leonhard Euler Foundation}} Scholarship, Russia, 2008
\end{compactitem}
\par\quad\par\smallskip 

\textbf{SERVICE} \par\smallskip
\textbf{To the profession and broader community:}
\begin{compactitem}
\item Grant reviewer/panelist for NSF and the Simons Foundation
\item Referee for several book series and multiple journals, including Inventiones, Duke, etc.
\item Advisory committee member, \emph{Poisson} conference series
\item Guest editor of the Arnold Mathematical Journal (special issue on finite dimensional integrable systems, in preparation)
\item Co-organizer of the \emph{Lie groups, geometry, integrability, hydrodynamics} conference, Nordfjordeid, Norway, 2024
\item Co-organizer of the virtual Hamiltonian Systems Seminar, 2020 - present
\item Co-organizer of the Tucson Math Circle, 2023 - 2024
%\item Organizer of {Integrable Systems and Algebraic Geometry Learning Seminar}, Moscow State
%University, 2014
%\item Co-organizer of {Modern Geometric Methods Seminar}, Moscow State University, 2012 - 2014
\end{compactitem}
 \par\smallskip
\textbf{To the University of Glasgow:}
\begin{compactitem}
\item Co-organizer of the Integrable Systems and Mathematical Physics Seminar, 2025 - Present
\item Co-organizer of the joint Edinburgh-Glasgow Integrability Seminar, 2025 - Present
%\item Organizer of {Integrable Systems and Algebraic Geometry Learning Seminar}, Moscow State
%University, 2014
%\item Co-organizer of {Modern Geometric Methods Seminar}, Moscow State University, 2012 - 2014
\end{compactitem}
  \par\smallskip
\textbf{To the University of Arizona:}
\begin{compactitem}
\item Committee membership: Graduate (2020 - 2022),  Postdoctoral (2020 and 2022 - 2024), Personnel (2024 - 2025)
%\item Member of the Postdoctoral Committee, 2020 and 2022 - 2024
%\item Member of the Graduate Committee, 2020 - 2022
\item Coordinator of the Undergraduate Research Assistantship Program, 2020 - 2021
\item Co-chair of the {Mathematics Colloquium}, 2018 - 2019
%\item Organizer of {Integrable Systems and Algebraic Geometry Learning Seminar}, Moscow State
%University, 2014
%\item Co-organizer of {Modern Geometric Methods Seminar}, Moscow State University, 2012 - 2014
\end{compactitem}
 \par\smallskip
\textbf{To the University of Toronto:}
\begin{compactitem}
\item Organizer of the {Symplectic Geometry Seminar}, 2015 - 2016
%\item Organizer of {Integrable Systems and Algebraic Geometry Learning Seminar}, Moscow State
%University, 2014
%\item Co-organizer of {Modern Geometric Methods Seminar}, Moscow State University, 2012 - 2014
\end{compactitem}
%\item Referee for \textbf{Annals of Global Analysis and Geometry; Archive for Rational Mechanics and Analysis;
%Arnold Mathematical Journal; Discrete and Continuous Dynamical Systems; Journal of Geometry and Physics; Journal of Nonlinear
%Mathematical Physics; Nonlinearity; Philosophical Transactions of the Royal Society A; SIGMA}
\par\quad\par\smallskip
\textbf{GRADUATE STUDENTS} \par\smallskip
%\textbf{Postdocs:}
\begin{compactitem}
\item  Quinton Aboud, University of Arizona, PhD expected in 2025
\item Abigayle Dirdak, University of Arizona, PhD, 2024
\item Ilia Kirillov, University of Toronto, PhD, 2024 (co-advised with B.\,Khesin)
\item  Leaha Hand, University of Arizona, PhD, 2024
\item  Quinton Aboud, University of Arizona, MS, 2021
\item Abigayle Dirdak, University of Arizona, MS, 2021
\item Ilia Kirillov, Moscow State University, MS, 2019
\item Daniel Fusca, University of Toronto, PhD, 2018 (co-advised with B.\,Khesin)
\item Konstantin Aleshkin, Moscow State University, MS, 2015



%Aleshkin, Moscow State University, 2012 - 2015 %(thesis title: \textbf{Singularities of integrable systems
%on loop algebras and nodal curves})%\thispagestyle{empty}
\end{compactitem}
\par\quad\par
\textbf{POSTDOCS} \par\smallskip
%\textbf{Postdocs:}
\begin{compactitem}
\item Darlayne Addabbo, University of Arizona, 2020 - 2024 (now a TTAP at SUNY Poly)
\item Melinda Lanius, University of Arizona, 2018 - 2021 (now a TTAP at Auburn)
\end{compactitem}
%\par\smallskip
%\textbf{M.\,Sc. Students:}
%\begin{compactitem}
%\item Ilya Kirillov, Moscow State University, 2015 - now \item Konstantin
%Aleshkin, Moscow State University, 2012 - 2015 %(thesis title: \textbf{Singularities of integrable systems
%on loop algebras and nodal curves})%\thispagestyle{empty}
%\end{compactitem}
\par\quad\par
\textbf{INVITED CONFERENCE TALKS AND LECTURE SERIES}\par\smallskip
%\textbf{Upcoming conferences:}
%\begin{compactitem}
%\item Discrete
%Integrable Systems: Difference Equations, Cluster Algebras and
%Probabilistic Models, ICTS, Bangalore, India, 2024
%%\item\textbf{AMDS 2020: International Conference on Algebraic Methods in Dynamical Systems}, ENS de Lyon, November 2020
%% \item\textbf{FDIS 2021: Finite Dimensional Integrable Systems in Geometry and Mathematical Physics}, Tel Aviv University, June 2021
%\end{compactitem} \par\smallskip
\textbf{Conferences:}
\begin{compactitem}
\item Cluster Algebras and Mathematical Physics in the Lakes, University of Cumbria, 2025
\item Statistical Mechanics and Discrete Geometry, IPAM, Los Angeles, 2024
\item Infinite Dimensional Geometry and PDEs, Banff, 2023
%\item {FDIS 2023: Finite Dimensional Integrable Systems}, University of Antwerp,  2023
\item Math in the Mine: a workshop on shape spaces, Mini\`{e}re de Vallauria, France, 2023
\item Finite Dimensional Integrability in Mathematical Physics, Les Diablerets, 2023
\item JMM, Special Session on Integrable Systems and Symplectic Group Actions, Boston, 2023
\item {FDIS 2022: Finite Dimensional Integrable Systems}, Tel Aviv University,  2022
\item {AMS Fall Eastern Sectional Meeting,  Session on Geometric Dynamics},  Online, 2020
\item {FDIS 2019: Finite Dimensional Integrable Systems}, Shanghai Jiao Tong University,  2019
\item   {Cluster Algebra and Mathematical Physics}, Michigan State University,  2018
\item  {Geometric Aspects of Momentum Maps and Integrability},  CSF Ascona,  2018
\item   {Gone Fishing 2018: a meeting on Poisson geometry}, UC San Diego,  2018
\item {Analytic and Algebraic Methods in Differential Equations}, Moscow,
 2017
\item{Painleve Equations and Discrete Dynamics}, Banff,  2016
\item{Integrable Systems},  CSF Ascona, Switzerland,  2016
\item{Integrability and Near-Integrability in Mechanics and Geometry}, BIRS-Oaxaca,  2016
\item {Analysis of PDEs of Fluid Mechanics}, Rice University,  2016
\item {Integrability in Mechanics and Geometry}, ICERM,  2015
\item  {Beyond Toric Integrability}, EPFL,  2013
\end{compactitem}  \par\smallskip
\textbf{Lecture series:}

\begin{compactitem} \item {Infinite-dimensional Geometry and Integrable PDEs}, \emph{Infinite-dimensional Geometry: Theory and Applications} Thematic Program, Erwin Schr\"odinger Institute, 2025 \item {Poisson Geometry and Hydrodynamics}, \emph{Poisson} Summer School, Fields Institute, 2018
\end{compactitem}
\par\quad\par
%\textbf{Recent talks (since 2015)}
%\begin{longtable}{ p{3cm}p{13cm} }
%\centering June 2016 & 
%\textbf{Integrable Systems} conference, CSF Ascona, Switzerland\\
%\centering June 2016 & 
%\textbf{Integrability and Near-Integrability in Mechanics and Geometry} workshop, CMO-BIRS\\
%\centering May 2016 & 
%\textbf{Analysis of PDEs of Fluid Mechanics} workshop, Rice University\\
%\centering May 2016 & 
%{Symplectic \& Poisson Geometry Seminar}, University of Illinois at Urbana-Champaign\\
%
%\centering Apr 2016 &  
%{Infinite Dimensional Algebra Seminar}, MIT\\
%
%\centering Apr 2016 & 
%Analysis-Geometry Seminar, Northeastern University\\
%
%\centering Apr 2016 &  
%{Colloquium}, University of Texas Dallas\\
%\centering Mar 2016 & 
%{Geometry and Topology Seminar}, North Carolina State University\\
%\centering Mar 2016 & 
%{\textbf{Gone Fishing} Meeting in Poisson Geometry}, University of Colorado Boulder\\
%
%\centering Feb 2016 &  
%{Felix Klein Seminar}, University of Notre Dame\\
%\centering Jan 2016 &  
%{Colloquium}, College of Charleston\\
%\centering Nov 2015 &  
%{Geometry and Topology Seminar}, University of Wisconsin Madison\\
%\centering Nov 2015 & 
%{Applied Analysis Seminar}, Pennsylvania State University\\
%\centering July 2015 & 
%{Seminar on Integrable Systems}, SISSA\\
%\centering July 2015 &  
%\textbf{Finite Dimensional Integrable Systems} conference, Bedlewo, Poland\\
%\centering June 2015 & 
%\textbf{Integrability in Mechanics and Geometry} workshop, ICERM \\
%\centering Mar 2015 & 
%
%Joint Colloquium: Carleton University -- University of Ottawa\\
%\centering Feb 2015 & 
%Seminar Physique Math\'{e}matique, CRM (Montreal, Canada) 
%\end{longtable}
%\thispagestyle{empty}
%\begin{center}
%%{\centering{ \Large List of Publications}}
%\end{center}\par\quad\par\smallskip
%\renewcommand{\baselinestretch}{1}
\textbf{PAPERS} \par\smallskip
 \textbf{Preprints:}
 \begin{compactenum}
 
 \item Folding of quadrilaterals, zigzags, and Arnold-Liouville integrability\\  	\textit{Arnold Mathematical Journal}, to appear 
   \item 	Pentagram maps over rings, Grassmannians, and skewers, with L.\,Hand \\ \textit{Journal of the  European Mathematical Society}, to appear
 
 \item 	Planar networks and simple Lie groups beyond type A \\ \textit{Advances in Mathematics}, to appear
 





\end{compactenum}
 \par\smallskip
 \textbf{Papers:}
\begin{compactenum}


\item Coadjoint orbits of area-preserving diffeomorphisms of non-orientable surfaces, with B.\,Khesin and I.\,Kirillov	\\	\textit{Journal of Symplectic Geometry}, vol. 23, no. 1, pp. 1-35, 2025


\item Integrable systems and cluster algebras, with M.\,Gekhtman \\ \textit{Encyclopedia of Mathematical Physics 2nd edition,} 2024

 \item {Geometry of generalized fluid flows}, with B. Khesin \\ \textit{Calculus of Variations and Partial Differential Equations}, vol. 63, no. 3, 2024

 
  \item Change of polytope volumes under M\"obius transformations and the circumcenter of mass\\ \textit{Discrete \& Computational Geometry}, vol. 72, pp. 1369-1376, 2024

 \item {Long-diagonal pentagram maps}, with B. Khesin \\ 	\textit{Bulletin of the London Mathematical Society}, vol .55, no. 3, pp. 1314-1329, 2023


 
  \item {Polygon recutting as a cluster integrable system}\\ \textit{Selecta Mathematica}, vol. 29, no. 21, 2023
 
 \item {Jordan-Kronecker invariants of Lie algebra representations and degrees of invariant polynomials}, with A.\,Bolsinov and I.\,Kozlov\\\textit{Transformation Groups}, vol. 28, pp. 541-560, 2023
 
  \item {What is a lattice W-algebra}, with G. Mar\'i Beffa		\\\textit{International Mathematics Research Notices},  no. 19,  pp. 17021-17059, 2023
 
  \item {Dimers, networks, and cluster integrable systems}\\\textit{Geometric and Functional Analysis}, vol. 32, pp. 861-880, 2022

 \item {The pentagram map, Poncelet polygons, and commuting difference operators}\\\textit{Compositio Mathematica},  vol. 158, no. 5, pp. 1084-1124, 2022
 \item {Pentagram maps and refactorization in Poisson-Lie groups}\\\textit{Advances in Mathematics}, vol. 404, 
p. 108476,  2022

\item {Intersecting the sides of a polygon}\\\textit{Proceedings of the American Mathematical Society}, vol. 150, pp. 639-649, 2022
\item {The limit point of the pentagram map and infinitesimal monodromy}, with Q.\,Aboud\\\textit{International Mathematics Research Notices}, no. 7, pp. 5383-5397, 2022
\item {Smooth invariants of focus-focus singularities and obstructions to product decomposition}, with
A. Bolsinov\\\textit{Journal of Symplectic Geometry}, vol. 17, no. 6, pp. 1613-1648, 2019
\item {Vortex sheets and diffeomorphism groupoids}, with B. Khesin\\\textit{Advances in Mathematics}, vol. 338, pp. 447-501, 2018
\item {Characterization of steady solutions to the 2D Euler equation}, with B. Khesin\\\textit{International
Mathematics Research Notices},  no. 24, pp. 7459-7503, 2017
\item {Singularities of integrable systems and algebraic curves}\\\textit{International Mathematics Research
Notices},  no. 18, pp. 5475-5524, 2017
\item {Classification of Casimirs in 2D hydrodynamics}, with B. Khesin\\\textit{Moscow Mathematical
Journal}, vol. 17, pp. 699-716, 2017
\item {Finite-dimensional integrable systems: a collection of research problems}, with A. Bolsinov and
D. Tsonev\\\textit{Journal of Geometry and Physics}, vol. 115, pp. 2-15, 2017
\item {Euler equations on the general linear group, cubic curves, and inscribed hexagons}, with
K. Aleshkin\\\textit{L'Enseignement Math\'ematique}, vol. 62, pp. 143-170, 2016 
\item {Coadjoint orbits of symplectic diffeomorphisms of surfaces and ideal hydrodynamics}, with
B. Khesin and M. Mousavi\\\textit{Annales de l'Institut Fourier}, vol. 66, no. 6, pp. 2385-2433, 2016
\item {Pentagrams, inscribed polygons, and Prym varieties}\\\textit{Electronic Research Announcements in
Mathematical Sciences}, vol. 23, pp. 25-40, 2016
\item {{Flat bi-Hamiltonian structures and invariant densities}}\\\textit{Letters in Mathematical Physics},  vol. 106, pp. 1415-1427, 2016
\item {{Leapfrog map and Toda lattice}}, appendix to {{Integrable cluster dynamics of directed networks and pentagram maps}} by M.\,Gekhtman, M.\,Shapiro, S.\,Tabachnikov,  and A.\,Vainshtein\\\textit{Advances in Mathematics}, vol. 300, pp. 390-450, 2016
\item {{Algebraic geometry and stability for integrable systems}}\\\textit{Physica D}, {vol. 291}, pp. 74-82, 2015
\item {{Singularities of bi-Hamiltonian systems}}, with A.\,Bolsinov \\
\textit{Communications in Mathematical Physics}, {vol. 331}, pp. 507-543, 2014
\item {{Stability of relative equilibria of multidimensional rigid body}}\\\textit{Nonlinearity}, vol. 27, pp. 1419-1444, 2014
\item {{The derived algebra of a stabilizer, families of coadjoint orbits, and sheets}}\\\textit{Journal of Lie Theory}, {vol. 24}, pp. 705-714, 2014
\item {{Curvature of Poisson pencils in dimension three}}\\\textit{Differential Geometry and its Applications}, {vol. 31}, pp. 557-567, 2013
\item {{Stability of stationary rotations of multidimensional rigid body}}\\\textit{Moscow University Mathematics Bulletin}, {vol. 68}, pp. 80-82, 2013
\item {{Stability in bihamiltonian systems and
multidimensional rigid body}}\\\textit{Journal of Geometry and Physics}, {vol. 62}, pp. 2414-2423, 2012
\item {{A note on relative equilibria of a free
multidimensional rigid body}}\\\textit{Journal of Physics A: Mathematical and Theoretical}, {vol. 45}, p. 325203, 2012
\item {Algebra and topology of integrable systems: problems for investigation}, with A.\,Bolsinov, A.\,Konyaev, and A.\,Oshemkov\\\textit{Tr. Sem. Vektor Tenzor Anal.}, {vol. 28}, pp. 119-191, 2012 (in Russian)
\item {{Classification of almost toric singularities of Lagrangian foliations}}\\\textit{Sbornik: Mathematics}, {vol. 202}, pp. 1021-1042, 2011
\item {{Smooth invariants of focus-focus singularities}} \\
\textit{Moscow University Mathematics Bulletin}, {vol. 66}, pp. 178-180, 2011
\end{compactenum}

%\par\smallskip
%\textbf{Unpublished notes:}
%\begin{compactenum}
%\item {Matrix polynomials, generalized Jacobians, and graphical zonotopes}, arXiv:1506.05179
%\item {Singularities of integrable systems and nodal curves}, arXiv:1408.4844
%\item {Generalized argument shift method and complete commutative subalgebras in polynomial Poisson
%algebras}, arXiv:1406.3777
%\end{compactenum}
\end{document}